---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# MPhS
<!-- badges: start -->
<!-- badges: end -->

With the `MPhS` package, the user can map their transcriptomic dataset onto the Molecular Phenology Scale (MPhS) proposed by

Tornielli GB, Sandri M, Fasoli M, Amato A, Pezzotti M, Zuccolotto P, Zenoni S (2023) 
A molecular phenology scale of grape berry development. Horticulture Research, Volume 10, Issue 5:uhad048.
<a href="https://academic.oup.com/hr/article/10/5/uhad048/7077841" target="_blank">doi:10.1093/hr/uhad048</a>

## Installation

You can install the development version of MPhS from [GitHub](https://github.com/sndmrc/MPhS) with:

``` r
# install.packages("pak")
pak::pak("sndmrc/MPhS")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(MPhS)
## basic example code
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
